---
title: "notes"
author: "CNBI"
format: html
editor: visual
---

```{r}
library(ggplot2)
```

## Simulation

### Results

#### Power, sample sizes and effect sizes

```{r}
# Data
figure1_data_set2 <- readRDS("~/GitHub/SSD-xo-CRT/data/figure1_data/figure1_data_set2.RDS")
```

```{r}
# Number of clusters
ggplot(figure1_data_set2[figure1_data_set2$fixed == "n2",],
       aes(
           y = eta.BF12,
           x = n2.final,
           color = as.factor(eff_size),
           shape = as.factor(eff_size)
       )) +
    geom_point() + geom_line() +
    scale_color_brewer(palette = "Dark2") + scale_fill_brewer(palette = "Dark2") +
    labs(title = "Bayes Factor H1 vs Hc",
         color = "Effect size",
         shape = "Effect size") +
    xlab("Number of clusters") + ylab("Probability") + theme(legend.position = "bottom") + geom_hline(yintercept=figure1_data_set2$eta)
```

Note: Number of clusters instead of cluster size because for these number of clusters 5 participants per cluster was enough.

```{r}
# Cluster size
ggplot(figure1_data_set2[figure1_data_set2$fixed == "n1",],
       aes(
           y = eta.BF12,
           x = n1.final,
           color = as.factor(eff_size),
           shape = as.factor(eff_size)
       )) +
    geom_point() + geom_line() +
    scale_color_brewer(palette = "Dark2") + scale_fill_brewer(palette = "Dark2") +
    labs(title = "Bayes Factor H1 vs Hc",
         color = "Effect size",
         shape = "Effect size") +
    xlab("Cluster size") + ylab("Probability") + theme(legend.position = "bottom") + geom_hline(yintercept=figure1_data_set2$eta)


```

In comparison to the increase of number of clusters, in this case there is a small difference of Probabilty across the effect sizes when the cluster size is small. It is possible to see the curve.

#### Power and correlations (ICC_bp and CAC)

```{r}
figure2_data_set2 <- readRDS("~/GitHub/SSD-xo-CRT/data/figure2_data/figure2_data_set2.RDS")
```

```{r}
ggplot(figure2_data_set2[figure2_data_set2$fixed == "n2",],
       aes(
           y = eta.BF12,
           x = n2.final,
           color = as.factor(cac),
           shape = as.factor(cac)
       )) +
    geom_point() + geom_line() +
    facet_grid(cols = vars(wp_icc)) +
    scale_color_brewer(palette = "Dark2") + scale_fill_brewer(palette = "Dark2") +
    labs(title = "Bayes Factor H1 vs Hc",
         color = "CAC",
         shape = "CAC") +
    xlab("Number of clusters") + ylab("Probability") + theme(legend.position = "bottom") + geom_hline(yintercept=figure2_data_set2$eta)
```

When the within cluster between-period correlation coefficient is small, the difference between the cluster autocorrelation is so small that is not perceived in the Figure. In comparison, when the cluster between-period correlation coefficien, the difference in Bayesian power across the different values of cluster autocorrelation increases, specially for smaller number of clusters such as 10 and 20.

```{r}
ggplot(figure2_data_set2[figure2_data_set2$fixed == "n1",],
       aes(
           y = eta.BF12,
           x = n1.final,
           color = as.factor(cac),
           shape = as.factor(cac)
       )) +
    geom_point() + geom_line() +
    facet_grid(cols = vars(wp_icc)) +
    scale_color_brewer(palette = "Dark2") + scale_fill_brewer(palette = "Dark2") +
    labs(title = "Bayes Factor H1 vs Hc",
         color = "CAC",
         shape = "CAC") +
    xlab("Cluster size") + ylab("Probability") + theme(legend.position = "bottom") + geom_hline(yintercept=figure2_data_set2$eta)

```

In comparison to the previous Figure, in this Figure the differences in empirical $\eta$ across the levels of CAC are smaller. Only when the within-cluster between-period correlation is larger such as 0.1, then there are some differences in the empirical $\eta$ for smaller cluster sizes such as 5 and 10. After 10 the differences are not distinguishable.

#### Power, Bayes factor threshold and eta

```{r}
figure3_data_set2 <- readRDS("~/GitHub/SSD-xo-CRT/data/figure3_data/figure3_data_set2.RDS")
```

```{r}
# Number of clusters
ggplot(figure3_data_set2[figure3_data_set2$fixed == "n2",],
       aes(
           y = eta.BF12,
           x = n2.final,
           color = as.factor(BF_thresh),
           shape = as.factor(BF_thresh)
       )) +
    geom_point() + geom_line() +
    facet_grid(cols = vars(eta)) +
    scale_color_brewer(palette = "Dark2") + scale_fill_brewer(palette = "Dark2") +
    labs(title = "Bayes Factor H1 vs Hc",
         color = "BF threshold",
         shape = "BF threshold") +
    xlab("Number of clusters") + ylab("Probability") + theme(legend.position = "bottom")
```

According to the plots there is a clear difference across the Bf thresholds, it is easier to meet the power criterion when the threshold is smaller, for instance 3.

```{r}
# Cluster size
ggplot(figure3_data_set2[figure3_data_set2$fixed == "n1",],
       aes(
           y = eta.BF12,
           x = n1.final,
           color = as.factor(BF_thresh),
           shape = as.factor(BF_thresh)
       )) +
    geom_point() + geom_line() +
    facet_grid(cols = vars(eta)) +
    scale_color_brewer(palette = "Dark2") + scale_fill_brewer(palette = "Dark2") +
    labs(title = "Bayes Factor H1 vs Hc",
         color = "BF threshold",
         shape = "BF threshold") +
    xlab("Cluster size") + ylab("Probability") + theme(legend.position = "bottom")


```

In comparison to the other Figure, the empirical $\eta$ tends to be lower for all combinations. Moreover, there is a clearer distinction in the empirical $\eta$ across the different values of thresholds. As expected, with larger thresholds the empirical $\eta$ is lower.

#### Full factorial simulation

```{r}
full_sim_data_set2 <- readRDS("~/GitHub/SSD-xo-CRT/data/set2_data/full_sim_data_set2.RDS")
```

```{r}
# Function to make the plots faster
plot_simulation_grid <- function(data, 
                                 fixed_param = "n2", 
                                 target_eta = 0.80, 
                                 palette = "Dark2") {
    
    # Select the correct x-axis variable based on fixed parameter design
    x_var <- if (fixed_param == "n2") "n2.final" else "n1.final"
    x_label <- if (fixed_param == "n2") "Number of Clusters (n2)" else "Cluster Size (n1)"
    
    plot_df <- subset(data, fixed == fixed_param & eta == target_eta)
    
    ggplot(plot_df, aes(
        x = .data[[x_var]], 
        y = eta.BF12, 
        color = factor(wp_icc), 
        linetype = factor(cac),
        shape = factor(cac),
        group = interaction(wp_icc, cac)
    )) +
        geom_hline(yintercept = target_eta, linetype = "dotted", color = "grey40", linewidth = 0.7) +
        geom_line(linewidth = 0.8) +
        geom_point(size = 2) +
        facet_grid(
            rows = vars(BF_thresh), 
            cols = vars(eff_size), 
            labeller = label_both,
            scales = "free_x"
        ) +
        scale_color_brewer(palette = palette) +
        scale_y_continuous(limits = c(0.7, 1), breaks = seq(0, 1, 0.2)) +
        labs(
            title = paste0("Probability of Exceeding BF Threshold (Fixed: ", fixed_param, ", Target η = ", target_eta, ")"),
            x = x_label,
            y = "P(BF > Threshold)",
            color = "Within-Period ICC",
            linetype = "CAC",
            shape = "CAC"
        ) +
        theme_bw(base_size = 11) +
        theme(
            legend.position = "bottom",
            legend.box = "horizontal",
            strip.background = element_rect(fill = "grey92"),
            panel.grid.minor = element_blank()
        )
}
```

```{r}
plot_simulation_grid(full_sim_data_set2, fixed_param = "n2", target_eta = 0.70)
plot_simulation_grid(full_sim_data_set2, fixed_param = "n1", target_eta = 0.70)
plot_simulation_grid(full_sim_data_set2, fixed_param = "n2", target_eta = 0.80)
plot_simulation_grid(full_sim_data_set2, fixed_param = "n1", target_eta = 0.80)
plot_simulation_grid(full_sim_data_set2, fixed_param = "n1", target_eta = 0.90)
plot_simulation_grid(full_sim_data_set2, fixed_param = "n2", target_eta = 0.90)
plot_simulation_grid(full_sim_data_set2, fixed_param = "n2", target_eta = 0.95)
plot_simulation_grid(full_sim_data_set2, fixed_param = "n1", target_eta = 0.95)

```
